---
title: "HW2"
output: html_document
date: "2025-03-10"
name: Bo Peng

output:
  html_document:
    df_print: paged
  word_document: default
---


# A procedure to calculate $\theta$ values

### 3. Calculate the Fst value for each site and visualize the results


```{r, eval=FALSE}
library("data.table")
geno <- fread("/Users/bopeng/Documents/GitHub/PopGen_HW/largedata/snp_calls.txt", header=FALSE)
names(geno) <- c("chr", "pos", "ref", "alt", "quality", "depth", paste0("T",1:5), paste0("L", 1:5))


for (i in 7:16) {
  # Extract the column name
  nm <- names(geno)[i]
  
  # Extract allele 1
  geno[[paste0(nm, "_a1")]] <- gsub("/.*", "", geno[[i]])
  
  # Extract allele 2
  geno[[paste0(nm, "_a2")]] <- gsub(".*/", "", geno[[i]])
}

```

---

# A procedure to calculate $\theta$ values

### 3. Calculate the Fst value for each site and visualize the results

#### Compute p1, p2, p

geno[geno == "."] <- NA
```{r, eval=FALSE}
# Convert all relevant columns to numeric safely
geno[, 17:36] <- lapply(geno[, 17:36, with = FALSE], function(col) as.numeric(as.character(col)))

geno$p <- apply(geno[, 17:36], 1, function(x) { sum(x==0)/(sum(x==1) + sum(x==0))})
geno$p <- geno$p/10

geno$p1 <- apply(geno[, 17:26], 1, function(x) {sum(x==0)/(sum(x==1) + sum(x==0))})
geno$p1 <- geno$p1/5

geno$p2 <- apply(geno[, 27:36], 1, function(x) {sum(x==0)/(sum(x==1) + sum(x==0))})
geno$p2 <- geno$p2/5
```

Then finally,

```{r, eval=FALSE}
geno$fst <- with(geno, ((p1-p)^2 + (p2-p)^2)/(2*p*(1-p)) )
```

Output the Fst results


```{r, eval=FALSE}
write.table(geno, "/Users/bopeng/Documents/GitHub/PopGen_HW/cache/fst.csv", sep=",", row.names = FALSE, quote=FALSE)
```

---
# A procedure to calculate $\theta$ values

### 3. Calculate the Fst value for each site and visualize the results

#### Visualize the results on my local computer

```{r, eval=FALSE}
fst <- read.csv("/Users/bopeng/Documents/GitHub/PopGen_HW/cache/fst.csv")

plot(fst$pos, fst$fst, xlab="Physical position", ylab="Fst value", main="")
```

```{r, eval=FALSE}

hist(fst$fst, xlab = "Fst value", main = "Histgram of Fst", col = "Blue", border = "White")

```






